\documentclass[letterpaper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{ragged2e}
\usepackage{changepage}

\usepackage{enumitem} % allows customizing itemize
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}




\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}


\urlstyle{same}


\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]


% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1


%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
     
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}




\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}


\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}




\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    {\Huge \scshape Priyanshu Gupta} \\ \vspace{1pt}
    Jalandhar,  Punjab \\ \vspace{3pt}
    \small 
    \small \href{9888168884}{ \raisebox{-0.1\height}\faPhone\ \underline{9888168884} ~} 
    \href{p.gupta98156@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{p.gupta98156@gmail.com}} ~
    \href{https://www.linkedin.com/in/priyanshu-gupta18/}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{LinkedIn}}  ~
    \href{https://github.com/Priyanshu98156}{\raisebox{-0.2\height}\faGithub\ \underline{Github}} ~
\end{center}

\section{Profile}
Highly ambitious Data Analyst with advanced Python and data analysis skills seeks an entry-level position.  Developed a machine learning model leveraging CNN, achieving 90\% accuracy in tumor detection within a medical imaging project (MedVision). Proficient in Excel, MySQL, and Python; eager to contribute data-driven insights and automate reporting processes.\\ 


\section*{Education}
\textbf{B.tech (Computer Science Engineering)} \\[2pt]
DAV Institute of Engineering \& Technology, Jalandhar, Punjab \hfill 2023 -- 2026 \\[2pt]
CGPA/Percentage: 8.2 \\[6pt]
\textbf{Diploma (Computer Science \& Engineering)} \\[2pt]
Mehr Chand Polytechnic College, Jalandhar, Punjab \hfill 2020 -- 2023 \\[2pt]
CGPA/Percentage: 80 \\[6pt]


\section*{Technical Skills}
\textbf{Languages}: Python, Java, C++, C, Kotlin \\[4pt]
\textbf{Frameworks}: Xml, Streamlit, Tkinter \\[4pt]
\textbf{Tools}: Git, JupyterNotebook, VScode \\[4pt]


\section*{Projects}
\textbf{Medvision} \href{https://github.com/Priyanshu98156}{\faExternalLink} | \textit{Cnn, Tensorflow, Python, Numpy, Pandas} \hfill May 2025 \\[2pt]
\begin{adjustwidth}{0.5cm}{0cm}
Developed a brain tumor prediction system (Medvision) using a CNN implemented with TensorFlow, Python, NumPy, and Pandas.  This image classification model accurately identifies the presence of brain tumors in MRI scans, providing a critical diagnostic tool.  The project leveraged advanced neural network techniques for efficient and accurate tumor detection.
\end{adjustwidth}
\vspace{6pt}
\textbf{Covid Insight} \href{https://github.com/Priyanshu98156}{\faExternalLink} | \textit{Python, Numpy, Pandas, Streamlit,  Matplotlib, Seaborn} \hfill Aug 2024 \\[2pt]
\begin{adjustwidth}{0.5cm}{0cm}
Developed a data visualization dashboard using Python (NumPy, Pandas, Matplotlib, Seaborn, and Streamlit) to analyze a COVID-19 dataset.  The project effectively communicated the pandemic's impact through interactive graphs, charts, and histograms, providing clear insights into key trends and patterns. This resulted in a readily accessible and informative resource for understanding the data.
\end{adjustwidth}
\vspace{6pt}
\textbf{House Price Prediction} \href{https://github.com/Priyanshu98156}{\faExternalLink} | \textit{Python, Numpy, Pandas, Streamlit} \hfill March 2025 \\[2pt]
\begin{adjustwidth}{0.5cm}{0cm}
Developed a house price prediction model using XGBoost and Random Forest algorithms, achieving over 90\% accuracy.  Leveraged Python, NumPy, Pandas, and Streamlit to clean, analyze, and process the dataset, resulting in a robust predictive model. This project demonstrated proficiency in data manipulation, machine learning model implementation, and deployment using a streamlined user interface.
\end{adjustwidth}
\vspace{6pt}


\section{CERTIFICATIONS}
$\sbullet[.75] \hspace{0.1cm}$ Kotlin Beginner to Advanced - Udemy \\
$\sbullet[.75] \hspace{0.1cm}$ Python and Data Science - O7 Services \\
$\sbullet[.75] \hspace{0.1cm}$ Machine learning Using Python \\

\section{ACHIEVEMENTS}
\begin{itemize}[leftmargin=*]
\item Achieved first place in college-organized hackathon.
\item Completed over 300 LeetCode coding challenges.
\end{itemize}


\end{document}